---
title       : Cockroft Gault calculator
subtitle    : A handy way to calculate renal function
author      : Leonardo Tozzi
job         : MD
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The Cockroft Gault formula

My Shiny application calculates creatinin clearance based on the Cockroft Gault equation.

Creatinin clearance is an important marker of renal function and a value <75 ml/min suggests renal failure. 

---

## How to use

As an input, you need to enter:

1. Age in years
2. Weight in kilos
3. Plasma creatinin in mg/dl 
4. Sex of your patient


--- 
## Example - Male

Age=50

Weight=75

Plasma creatinin=1.3

Sex=male

```{r ex1}
age=50
weight=75
creatinine=1.3
Clearance = (140-age)*weight/(72*creatinine)
Clearance
```


---
## Example - Female

Age=50

Weight=75

Plasma creatinin=1.3

Sex=male

```{r ex2}
age=50
weight=75
creatinine=1.3
Clearance = 0.85*(140-age)*weight/(72*creatinine)
Clearance
```
